\documentclass{beamer}
%\usetheme{default}    
\usetheme{Berkeley}    
\usecolortheme{crane}

\title{Consistency in the Cloud II}
\subtitle{Consistency v. Latency in Geo-Replicated Systems}
\author{Satabdi Aditya and Shannon Harwick}
\institute{University of Illinois at Chicago}
\titlegraphic{}
\date{\today}

\begin{document}


% --------------------------------------------------- Slide --
\begin{frame}[plain]
  \titlepage
\end{frame}



% --------------------------------------------------- Slide --

\section{Li et al.} 

\begin{frame}
\frametitle{Paper 1: Li et al.}

\textbf{Title} \newline
\textit{Source} \newline
Authors\newline
Date\newline

\end{frame}


% --------------------------------------------------- Slide --

\begin{frame}
\frametitle{Overview}

\begin{theorem}<1->
Every finite distributive lattice can be embedded in a boolean lattice.
\end{theorem}
\begin{proof}<3->
Use join-irreducible elements.
\end{proof}
\end{frame}



% --------------------------------------------------- Slide --
\begin{frame}
\frametitle{Example 2}
\begin{itemize}
\pause \item a local maximum, or % Each \pause creates a new slide within the frame.
\pause \item a local minimum, or
\pause \item an inflection point.
\end{itemize}  
\end{frame}



%%% BEGIN SHANNON SECTION %%%
% --------------------------------------------------- Slide --

\section{Lloyd et al.} 

\begin{frame}
\frametitle{Paper 2: Lloyd et al.}

\textbf{Stronger Semantics for Low-Latency Geo-Replicated Storage} \newline
\textit{Proceedings of the 10th USENIX Symposium on Networked Systems Design and Implementation (NSDI’13)} \newline
Wyatt Lloyd, Michael J. Freedman, Michael Kaminsky, and David G. Andersen \newline
April 2013 \newline

\end{frame}

% --------------------------------------------------- Slide --
\begin{frame}
\frametitle{Main Idea}
\begin{itemize}

\pause \item Take slight hit in throughput to get stronger version of consistency
\pause \item Causal Consistency Instead of Eventual Consistency (causal is stronger)
\pause \item We require low latency
\pause \item Extend previous systems: Cassandra and COPS

\end{itemize}  
\end{frame}

% --------------------------------------------------- Slide --
\begin{frame}
\frametitle{Contributions}
\begin{itemize}
\pause \item Eiger
	\begin{itemize}
		\item Low Latency
		\item High throughput (slightly lower than Cassandra)
		\item Causal Consistency (rather than eventual as in Cassandra)
	\end{itemize}
\pause \item Read Only Algorithm
\pause \item Write Only Algorithm
\end{itemize}  
\end{frame}

% --------------------------------------------------- Slide --
\begin{frame}
\frametitle{Background}
\begin{itemize}
\pause \item Cassandra
	\begin{itemize}
		\item Eventual Consistency
	\end{itemize}
\pause \item COPS
\end{itemize}  
\end{frame}

% --------------------------------------------------- Slide --
\begin{frame}
\frametitle{Consistency - Causal versus Eventual}
\begin{itemize}
\pause \item p1	
\end{itemize}  
\end{frame}

% --------------------------------------------------- Slide --
\begin{frame}
\frametitle{Column Family Data Model}
\begin{itemize}
\pause \item p1 % Each \pause creates a new slide within the frame.
\pause \item p2
\pause \item p3
\end{itemize}  
\end{frame}



% --------------------------------------------------- Slide --
\begin{frame}
\frametitle{Eiger}
\begin{itemize}
\pause \item p1 % Each \pause creates a new slide within the frame.
\pause \item p2
\pause \item p3
\end{itemize}  
\end{frame}

% --------------------------------------------------- Slide --
\begin{frame}
\frametitle{Evaluation}
\begin{itemize}
\pause \item Versus Cassandra
		\begin{itemize}
			\item Within 7\% of throughput Using Facebook-like data
			\begin{itemize}
				\item Ops/sec
				\item Keys/sec
				\item Columns/sec
			\end{itemize}
		\end{itemize}
\pause \item Versus COPS
		\begin{itemize}	
			\item Both have low latency
			\item Eiger has slightly higher latency due to 2nd round indirection
			\item Only Eiger has write transactions
			\item Eiger has less overhead because it tracks only one-hop dependencies
		\end{itemize}
\end{itemize}  
\end{frame}

% --------------------------------------------------- Slide --
\begin{frame}
\frametitle{Follow Up Research}
\begin{itemize}
\pause \item Mahajan et al. showed that Causal Consistency strongest that guarantees low latency.
\end{itemize}  
\end{frame}

% --------------------------------------------------- Slide --
\begin{frame}
\frametitle{Ideas for Future Research}
\begin{itemize}
\pause \item p1 
\end{itemize}  
\end{frame}


% --------------------------------------------------- Slide --

\section{Bibliography} 

\begin{frame}
\frametitle{Bibliography}


%%% SHANNON'S REFERENCES
\begin{itemize}
\item \textbf{Stronger Semantics for Low-Latency Geo-Replicated Storage}, 
\textit{Proceedings of the 10th USENIX Symposium on Networked Systems Design and Implementation (NSDI’13)}, 
Wyatt Lloyd, Michael J. Freedman, Michael Kaminsky, and David G. Andersen, 
April 2013

\item \textbf{Out in the Open: The Abandoned Facebook Tech That Now Helps Power Apple}, 
\textit{www.wired.com}
, Klint Finley, Aug. 4, 2014

\item \textbf{A Short Primer on Causal Consistency}, 
\textit{;login: The Usenix Magazine Volume 38, Number 4}, 
Wyatt Lloyd, Michael J. Freedman, Michael Kaminsky, and David G. Andersen, , August 2013


\end{itemize}  
\end{frame}




\end{document} 